Multidimensional signals and analytic flexibility: Estimating degrees of freedom in human speech analyses

### 2022-09-24 RR_manuscript/Draft_RR.Rmd
delete code that is no longer needed

# Team descriptives
#  - number of teams (initially)
#  - Avg size of each team
team_desc_df <- bind_rows(
  team_leaders %>% 
    group_by(leader) %>% 
    mutate(member_num = seq_along(ResponseId)) %>% 
    group_by(leader) %>% 
    mutate(n_members = max(member_num)) %>% 
    distinct(leader, n_members) %>% 
    ungroup() %>% 
    summarize(n_teams = nrow(.), 
              n_analysts = sum(n_members), 
              mean_size = mean(n_members), 
              sd_size = sd(n_members), 
              median_size = median(n_members)) %>% 
    mutate(stage = "Initial"), 
  team_leaders %>% 
    filter(leader %in% teams_on_osf) %>% 
    group_by(leader) %>% 
    mutate(member_num = seq_along(ResponseId)) %>% 
    group_by(leader) %>% 
    mutate(n_members = max(member_num)) %>% 
    distinct(leader, n_members) %>% 
    ungroup() %>% 
    summarize(n_teams = nrow(.), 
              n_analysts = sum(n_members), 
              mean_size = mean(n_members), 
              sd_size = sd(n_members), 
              median_size = median(n_members)) %>% 
    mutate(stage = "Submitted"), 
  team_leaders %>% 
    filter(leader %in% teams_used_in_analysis) %>% 
    group_by(leader) %>% 
    mutate(member_num = seq_along(ResponseId)) %>% 
    group_by(leader) %>% 
    mutate(n_members = max(member_num)) %>% 
    distinct(leader, n_members) %>% 
    ungroup() %>% 
    summarize(n_teams = nrow(.), 
              n_analysts = sum(n_members), 
              mean_size = mean(n_members), 
              sd_size = sd(n_members), 
              median_size = median(n_members), 
              min = min(n_members), 
              max = max(n_members)) %>% 
    mutate(stage = "Final")
  ) %>% 
  mutate_if(is.numeric, round, digits = 1)

@@

#tbl_model_desc <- msa_models_unique %>% 
#  select(animal, starts_with("n_")) %>% 
#  group_by(animal) %>% 
#  summarize(across(everything(), mean)) %>% 
#  pivot_longer(cols = -animal, names_to = "metric", values_to = "vals") %>% 
#  na.omit() %>% 
#  group_by(metric) %>% 
#  summarize(min = min(vals), max = max(vals), avg = mean(vals, na.rm = T), 
#            sd = sd(vals, na.rm = T)) %>% 
#  mutate(across(-c("metric", "avg", "sd"), round)) %>% 
#  mutate(across(c("avg", "sd"), specify_decimal, k = 1)) %>% 
#  mutate(desc = "model_desc", 
#    metric = fct_relevel(metric, "n_models"), 
#    `Mean (SD)` = glue::glue("{avg} ({sd})"), 
#    Range = glue::glue("{min} -- {max}"), 
#    Metric = case_when(
#      metric == "n_coefficients" ~ "n. coefficients", 
#      metric == "n_models" ~ "n. models", 
#      metric == "n_predictors" ~ "n. predictors", 
#      metric == "n_random" ~ "n. random effects", 
#      metric == "n_random_int" ~ "n. random intercepts", 
#      metric == "n_random_slo" ~ "n. random slopes", 
#      metric == "n_random_smooth" ~ "n. random smooths",
#      metric == "n_terms" ~ "n. terms"), 
#    label = glue::glue("{desc}_{metric}")) %>% 
#  select(label, desc, Metric, Min. = min, Max = max, `Mean (SD)`, avg, 
#    sd, Range) %>% 
#  mutate(across(-c("desc", "Metric"), as.character))

>>>>

# Team descriptives
#  - number of teams (initially)
#  - Avg size of each team
team_desc_df <- bind_rows(
  team_leaders %>% 
    group_by(leader) %>% 
    mutate(member_num = seq_along(ResponseId)) %>% 
    group_by(leader) %>% 
    mutate(n_members = max(member_num)) %>% 
    distinct(leader, n_members) %>% 
    ungroup() %>% 
    summarize(n_teams = nrow(.), 
              n_analysts = sum(n_members), 
              mean_size = mean(n_members), 
              sd_size = sd(n_members), 
              median_size = median(n_members), 
              min = min(n_members), 
              max = max(n_members)) %>% 
    mutate(stage = "Initial"), 
  team_leaders %>% 
    filter(leader %in% teams_on_osf) %>% 
    group_by(leader) %>% 
    mutate(member_num = seq_along(ResponseId)) %>% 
    group_by(leader) %>% 
    mutate(n_members = max(member_num)) %>% 
    distinct(leader, n_members) %>% 
    ungroup() %>% 
    summarize(n_teams = nrow(.), 
              n_analysts = sum(n_members), 
              mean_size = mean(n_members), 
              sd_size = sd(n_members), 
              median_size = median(n_members), 
              min = min(n_members), 
              max = max(n_members)) %>% 
    mutate(stage = "Submitted"), 
  team_leaders %>% 
    filter(leader %in% teams_used_in_analysis) %>% 
    group_by(leader) %>% 
    mutate(member_num = seq_along(ResponseId)) %>% 
    group_by(leader) %>% 
    mutate(n_members = max(member_num)) %>% 
    distinct(leader, n_members) %>% 
    ungroup() %>% 
    summarize(n_teams = nrow(.), 
              n_analysts = sum(n_members), 
              mean_size = mean(n_members), 
              sd_size = sd(n_members), 
              median_size = median(n_members), 
              min = min(n_members), 
              max = max(n_members)) %>% 
    mutate(stage = "Final")
  ) %>% 
  mutate_if(is.numeric, round, digits = 1)

@@
